Appendix B

### 2021-05-06 manuscript/bef_stability/appendixB.Rmd
Reviewed according to Maud's comments

---
title: Appendix B
subtitle: Species richness and food-web structure jointly drive community biomass and its temporal stability in fish assemblages 
author: Alain Danet, Maud Mouchet, Willem Bonnaffé, Elisa Thébault and Colin Fontaine
date: \today 
output:
  bookdown::pdf_document2:
    fig_caption: true 
    keep_tex: true
    toc: true
fontsize: 12pt
header-includes:
   - \usepackage{natbib}
   - \newcommand{\beginsupplement}{\setcounter{table}{2}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}} 
   - \usepackage{float}
   - \usepackage{booktabs}
   - \usepackage{makecell}
   - \usepackage{setspace}
   - \doublespacing
   - \usepackage{lineno}
   - \linenumbers
geometry: margin=2cm
bibliography: references.bib
number_sections: true
nocite: |
    @post_ecosystem_2000| @doi_resource_2009| @mchugh_dual_2010|
    @ogorman_unexpected_2017| @gauzens_biodiversity_2020| @dunne_network_2006|
    @mchugh_dual_2010| @doi_resource_2009| @allan_stream_2009|
    @petchey_predicting_2010| @winemiller_must_1989 | @galiana_spatial_2018 | @ogorman_simple_2019| @oksanen_exploitation_1981| @thebault_trophic_2005| @mccann_more_2009| @jiang_different_2009| @fussmann_ecological_2014| kratina_warming_2012
csl: ecology-letters.csl
---

@@

The monitoring of the fish communities occurs in streams varying in size, shape
and depth. The stream characteristics constrain the type of protocol that can be
applied. Small streams (depth < 0.7m across the entire width) are sampled with
the "complete" protocol. This protocol consists of placing anodes across the
entire width of the stream. As the fishermen made from one to three rows of
electric fishing, we selected only the data from the first row to homogenize the
sampling effort. In deeper and wider streams (depth >= 0.7m), the sampling is
partial over the bank and the channel and it is performed by boat and by foot
(along the bank). We selected only the sampling done over the bank because the
channel was not systematically sampled. Two types of partial protocols takes
place: "partial over bank" and "partial by points", which are respectively
continuous and discrete samplings. We considered both types of partial protocols
in our analysis. In the "partial by point" protocol, the channel was sometimes
sampled as well, so we selected only the "partial by point" sampling in which
all the sampling points were done over the bank to homogenize the sampling. Some
sampled stations were located in streams with intermediate characteristics where
both "complete" and "partial" protocols were alternatively used depending on the
state of the stream at the time of sampling. For these sites, we only kept the
samples that had been carried out with the most used protocol.

Heterogeneity in the sampling date may introduce variability in the fish
communities such as the presence of juveniles. In order to reduce heterogeneity
in the sampling date, only one sampling per year was retained if there were more
in a given year, the one that had the most species and then the most
individuals. Finally, most of the fish sampling occurred in September (Median:
mid-August) and the median standard deviation of the sampling month was inferior
to one (0.7) within stations, i.e. 3 weeks. To further reduce sampling
heterogeneity, we only kept the sampling in which the length of stream sampled
along the stream was inside the median length sampled more or less 30%.

@@

Once the fishes have been caught, they are divided into different batches (Fig.
\@ref(fig:p-body-size)). Each batch contains only one species but there may be
several batches for one species. The body size of the fishes is measured
differently for each type of batch.  There are four types of batches: N, I, S/L
and G. The batches N and I contain the biggest individuals. In the N and I
batches, the body size of all the individuals is recorded. The batches S/L
contain fishes of intermediate sizes.  Inside each S/L batch, the operator tries
to make batches as homogeneous as possible in terms of body size. Then, the body
size of a subsample of at least 20 individuals is recorded. The G batches
contain individuals of small body size, with care that body size is as
homogeneous as possible in a given batches.  Then body size of the shortest and
the longest individuals are recorded.

@@

Body size inference was guided by the recommendations of
the OFB agency, which has defined the sampling protocols, supervised the data
collection and performed analyses on the dataset for multiple purpose including stream
management.

@@

Batches that did not meet certain conditions were excluded. First, we also
excluded batches for which the total number of individuals was not recorded. We
also excluded G batches for which $l_{min} \geq l_{max}$ or if at least one of
the measurement was missing. Additionally, a given G batch was excluded when the
number of individuals felt below five, as G batches normally contained more
individuals. We finally excluded S/L batches for which the number of measured
individuals was inferior to 10, because it indicates a potential problem in the
batch. Finally, in the dataset used in the analysis, `r na_length` individuals
had missing length over `r nrow_fish_length` individuals, and body size was
inferred for these individuals.

@@

Some species were identified to subspecies, based on their morphotype, but they
belong to the same species based on fecundation criteria. We merged those
subspecies into one species. There was
`r length(unique(names(sp_to_replace())))` species to merge which belonged to 
`r length(unique(sp_to_replace()))` species.

@@

Diet information was obtained from fishbase.org and literature (Appendix A, Table S2). The
diet information contained from two to three life stages by species, the life
stages being defined by the body size of the fishes. Over the 57 fish species,
only seven had a piscivorous life stage and only three had a strict piscivorous
life stage. Fish species were then largely omnivorous.

@@

trophic_building_caption <- paste0( "Building of the metaweb. (1) Each
  species is divided into nine body size classes. We gathered information about
  the food diet of each fish species and how food diet varies according to
  ontogeny. (2) The life stage of a trophic species is determined by the
  median of the body size class, hereafter midpoint. A trophic link is set between the trophic
  species and the resources associated to this life stage. (3) For piscivorous
  trophic species, the trophic links among fishes are defined according to
  the predator/prey body size ratio. The predation window of a trophic
  species ranges from 3% to 45% of its midpoint. A trophic
  link is set between the predator trophic species and every trophic species whose
  midpoint of body size class range was included in the predation window.")

@@

```{r, cache = FALSE}
metaweb_caption <- paste0(
  "The metaweb describes the trophic interactions between all the 412 trophic species. Each trophic species is
  represented by a node and each color represents a species (S = 45). The seven
  resource nodes are drawn in grey. The species names corresponding to the
  three digit codes are found in Table S1."
)
```

```{r metaweb, cache = FALSE, fig.cap=metaweb_caption}
knitr::include_graphics(mypath("manuscript", "bef_stability", "figs", "metaweb.png"))
```

@@

Trophic interactions between the nodes of the metaweb were determined according to
the diet and the body size of the trophic species. `r length(removed_sp_metaweb)` 
species were removed because information about their diet was missing. It
represented  `r nrow(removed_ind_metaweb)` individuals over
`r nrow(length_sem_analysis)` individuals.

The life stage to which a trophic species belongs was determined by the median
of the body size range of the trophic species, each life stage being delimited
by a body size range. In turn, this trophic species has trophic interactions
with the resource nodes of its life stage. The trophic interactions between a
predator and a prey were determined by the predator-prey body size ratio
[@brose_predator_2019; @poisot_structure_2016; @schneider_body_2012]. For a
given trophic species, we first determined if its body size range overlapped
with a piscivorous life stage (Fig. \@ref(fig:p-net-inf)). If the trophic
species was piscivorous, we determined its prey size range from 3% to 45% of the
median of its size range. A trophic interaction was set for each trophic species
whose corresponding size class median felt into the prey range of the predator trophic
species (Fig. \@ref(fig:p-net-inf)). To sum up, the metaweb contains feeding interactions (1) between
trophic species, (2) between trophic species and resource nodes and (3) between
resource nodes.

@@

The procedures to obtain altitude, slope, width and depth of the streams are fully
explained in main text. Because those measurements were collected during the
fishing protocol, they were easier to manage in the analysis. Then, we detail
in the following sections how water temperature, water flow and Biological
Oxygen Demand (BOD) variables were obtained. The goal was to obtain an annual
mean for each variable, to match the yearly resolution of the fish monitoring.
Furthermore, the available data for these variables were measured at different
locations than the fish monitoring and then necessitates a step of spatial
interpolation.

@@

We modelled each variable, i.e. water temperature, water flow and BOD, as dependant only on the covariation between
sites taking in account the stream network. To model the autocovariance between
sites, we used the linear-sill and mariah functions for taildown and tailup
autocovariance, according to their predictive performance. The interpolations
were done with the `SSN` R package [@isaak_applications_2014; @hoef_ssn:_2014].

@@

The CV of biomass over time can cover multiple temporal dynamics, including
increases, stable, decreases and a mix of them. Theoretically, however, the CV
computed to quantify stability is often represented with the assumption that the
overall dynamic of the biomass varies around an equilibrium
[@kefi_advancing_2019]. In order to approach the condition of equilibrium, we
kept only the stations that show no clear temporal trends. To characterise the
biomass temporal dynamics according to their trajectories, we used the symbolic
aggregated approximation method (SAX), which is commonly used in time series
analysis and implemented in the `jmotif` R package [@senin_grammarviz_2018].
This method classifies time series rather than quantifies trends and so is
generic enough to encompass a diversity of temporal trajectories. The
classification necessitates three steps. The time series are first normalized. Then, we reduced the dimensionality of the time series by a Piecewise
Aggregation Approximation (PAA) method. Each time series is divided into $N$
frames of equal size that allows to reduce the dimensionality of the time
series. For each frame, we simply kept the mean value of the time series. The
last step is to qualify each frame into string. Because values of normalized
time series typically follows a normal distribution ($N(0,1)$), a breakpoint can
be computed by dividing the area under the normal distribution in equal parts.
The algorithm attributes an alphabetic letter to each part from the lowest to
the highest ($a$, $b$, $c$, ...). We set three breakpoints, so $a$, $b$ and $c$.
Finally, the trajectory of each time series is classified as a combination of
$a$, $b$, $c$ letters. $abc$ and $cba$ time series represent respectively
monotonic increasing and decreasing trajectories. For data analysis, we kept
only the $bbb$ which represent time series that showed no temporal tendencies,
with respect to our methodology.

@@

```{r, cache = FALSE, fig.pos = "!H", out.extra = ""}
sem_variable_table <- tibble(
  variable = c(paste0("PCA axis", seq(1, 2)), "Species richness", "Connectance", "Average trophic level", "Synchrony", "CVsp", "Total biomass"),
  unit = c(rep("unitless", 2), "# by square meter", rep("unitless", 4), "gram by square meter"
    ),
  transformation = c("Log base 10", "Log base 10 and inversion", "Log base 10", rep("No", 2), rep("Log base 10", 3)),
  description = c("linked to stream size",
    "linked to average temperature and BOD",
    "Total species richness over the temporal series",
    "Median of annual link density", "Median of annual average trophic level",
    "Temporal synchrony in the dynamics of population biomass", "Average
    variability of population biomass", "Median of annual total biomass")) %>%
kable(
  format = "latex",
  booktabs = T,
  caption = "The description of the variables used in the structural equation models."
  ) %>%
kable_styling(latex_options = c("striped", "scale_down"))
sem_variable_table
```

\begin{table}
\caption{\label{tab:hyp-sem} Presentation of the links 
of the Structural Equation Models associated with the references supporting the links.}
\begin{center}
\begin{tabular}{ m{7cm}| m{1cm}| m{6cm}}
    \hline
    Link & sign & reference\\
    \hline
    PCA1 Avg stream size $\to$ Species richness & (+) & Galiana et al. (2018) \\
    \hline
    PCA2 Avg temperature $\to$ Species richness & (+/-) & Woods et al. (2020); Gauzens et al. (2020) \\
    \hline
    PCA1 Avg stream size $\to$ Connectance & (-) & Galiana et al. (2018) \\
    \hline
    PCA2 Avg temperature $\to$ Connectance & (+/-) & O’Gorman et al. (2019);
    Oksanen et al. (1981)\\
    \hline
    Species richness $\to$ Connectance & (-) & Winemiller (1989); Dunne (2006) \\
    \hline
    PCA1 Avg stream size $\to$ Avg trophic level & (+) & Post et al. (2000); Doi et al. (2009); McHugh et al. (2010) \\
    \hline
    PCA2 Avg temperature $\to$ Avg trophic level & (+/-) & O’Gorman et al. (2017)\\
    \hline
    Species richness $\to$ Avg trophic level & (+) & Schneider et al. (2016)\\
    \hline
    Species richness $\to$ Synchrony & (-) & Thébault and Loreau (2005); Loreau and de Mazancourt (2008); Thibaut and Connolly (2013) \\
    \hline
    Connectance $\to$ Synchrony & (+) & Thébault and Loreau (2005)\\
    \hline
    Avg trophic level $\to$ Synchrony & (+) & Raimondo et al. (2004); McCann and Rooney (2009) \\
    \hline
    PCA1 Avg stream size $\to$ Synchrony & (-) & Wang et al. (2019)\\
    \hline
    PCA2 Avg temperature $\to$ Synchrony & (?) & \\
    \hline
    Species richness $\to$ CVsp & (+) & Jiang et al. (2009)\\
    \hline
    Connectance $\to$ CVsp & (+) & Thébault and Loreau (2005)\\
    \hline
    Avg trophic level $\to$ CVsp & (-) & McCann and Rooney (2009); Shanafelt and Loreau (2018)\\
    \hline
    PCA1 Avg stream size $\to$ CVsp & (?) & \\
    \hline
    PCA2 Avg temperature $\to$ CVsp & (+) & Kratina et al. (2012); Fussmann et al. (2014)\\
    \hline
    CVsp $\to$ Biomass stability & (-) & Thibaut and Connolly (2013)\\
    \hline
    Synchrony $\to$ Biomass stability & (-) & Thibaut and Connolly (2013)\\
    \hline
    Species richness $\to$ Total biomass & (+) & Schneider et al. (2016)\\
    \hline
    Connectance $\to$ Total biomass & (+/-) & Thébault & Loreau (2003); Poisot
    et al. (2013)\\
    \hline
    Avg trophic level $\to$ Total biomass & (+) & Wang and Brose (2018)\\
    \hline
    PCA1 Avg stream size $\to$ Total biomass & (+) & Post et al. (2000); Allan and Ibanez Castillo (2009); Doi et al. (2009)\\
    \hline
    PCA2 Avg temperature $\to$ Total biomass & (+/-) & Kratina et al. (2012);
    Tabi et al. (2019)\\
    \hline
    \end{tabular}
\end{center}
\end{table}

@@

```{r, cache = FALSE}
hist_var_caption <- paste0(
  "Distribution of the variables included in the Structural Equation Models. The
  biomass stability, the CV of species (CVsp), PCA1, PCA2, species richness,
  synchrony and total biomass were logged."
)
```

```{r hist-sem-data, cache = FALSE, fig.cap = hist_var_caption}
sem_data %>%
  select(log_bm_std, log_rich_tot_std, log_sync, log_stab_std, log_cv_sp, log_RC1, log_RC2, t_lvl, ct) %>%
  gather(variable, value) %>%
  mutate(variable = str_replace_all(variable, get_sem_var_name_replacement())) %>%
  ggplot(aes(x = value)) +
  geom_histogram() +
  facet_wrap(~variable, scales = "free")
```

@@

```{r mod-res, fig.width = 7, fig.asp = 2, fig.cap = caption_mod_res, cache = FALSE}
library(nlme)
plot_residuals <- function (x, y = "Diagnostic") {
  plot.lme(x, main = y, xlab = "Fitted values", ylab = "Residuals")
}
p_resid_stab_sem <- map2(mod_stab_list, names(mod_stab_list) , plot_residuals)
plot_grid(plotlist = p_resid_stab_sem, ncol = 2)
```

@@

```{r}
est_stab_sem_caption <- paste0(
  "Estimates of the effects of the studied variables as predicted by the
  structural equation model on the temporal stability of annual community
  biomass."

)

format_coef_table(stab_sem_rich) %>%
  mutate(Std.Estimate = cell_spec(Std.Estimate, bold = ifelse(P.Value <= 0.05, T, F), format = "latex", escape = F)) %>%
  kable(
    format = "latex",
    booktabs = T,
    caption = est_stab_sem_caption,
    escape = F 
    ) %>%
  collapse_rows(columns = 1, valign = "top") %>%
  kable_styling(latex_options = c("striped", "scale_down"))
```

```{r}
est_bm_sem_caption <- paste0(
    "Estimates of the effects of the studied variables as predicted by the
  structural equation model on the median of annual community
  biomass."
)

format_coef_table(bm_sem_rich) %>%
  mutate(Std.Estimate = cell_spec(Std.Estimate, bold = ifelse(P.Value <= 0.05, T, F))) %>%
kable(
  format = "latex",
  booktabs = T,
  caption = est_bm_sem_caption,
  escape = F 
  ) %>%
collapse_rows(columns = 1, valign = "top") %>%
kable_styling(latex_options = c("striped", "scale_down"))
```

@@

kable(formated_random_effects,
  format = "latex",
  booktabs = T,
  caption = caption_random_effect
  ) %>%
kable_styling(latex_options = c("striped"))
```

@@

```{r}
sens_cap <- paste0(
  "Sensivity analysis of the Structural Equation models for total biomass
  and its temporal stability."," The Constant dataset is the one keeping only the
  sites that does not show a clear temporal trend of community biomass; ", "Constant/
    without holes dataset kept only the constant sites plus the ones that had no
  holes in their sampling period; ", "Complete is the dataset containing all the
  sites that have been followed ten years or more", " Without holes dataset is
  the complete dataset but containing only the sites that had no holes in their sampling period."
)
```

```{r, fig.height = 8, fig.cap = sens_cap}
p_sens_bm <- plot_sensivity_analysis(
  .data = sem_bm_results,
  inverse_label_order = TRUE) +
  theme(legend.position = "none", plot.margin = unit(c(0, 0, 0, 25), units = "mm"))

>>>>

---
title: Appendix B
subtitle: Species richness and food-web structure jointly drive community biomass and its temporal stability in fish assemblages 
author: Alain Danet, Maud Mouchet, Willem Bonnaffé, Elisa Thébault and Colin Fontaine
date: \today 
output:
  bookdown::pdf_document2:
    fig_caption: true 
    keep_tex: true
    toc: true
fontsize: 12pt
header-includes:
   - \usepackage{natbib}
   - \newcommand{\beginsupplement}{\setcounter{table}{2}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}} 
   - \usepackage{float}
   - \usepackage[table]{xcolor}
   - \usepackage{multirow}
   - \usepackage{booktabs}
   - \usepackage{makecell}
   - \usepackage{setspace}
   - \doublespacing
   - \usepackage{lineno}
   - \linenumbers
geometry: margin=2cm
bibliography: references.bib
number_sections: true
nocite: |
    @post_ecosystem_2000| @doi_resource_2009| @mchugh_dual_2010|
    @ogorman_unexpected_2017| @gauzens_biodiversity_2020| @dunne_network_2006|
    @mchugh_dual_2010| @doi_resource_2009| @allan_stream_2009|
    @petchey_predicting_2010| @winemiller_must_1989 | @galiana_spatial_2018 | @ogorman_simple_2019| @oksanen_exploitation_1981| @thebault_trophic_2005| @mccann_more_2009| @jiang_different_2009| @fussmann_ecological_2014| kratina_warming_2012
csl: ecology-letters.csl
---

@@

The monitoring of the fish communities occurs in streams varying in size, shape
and depth. Stream characteristics constrain the type of protocol
applied. Small streams (depth < 0.7m across the entire width) are sampled with
the "complete" protocol. Anodes are distributed across the width of the river
then one to three electric fidhing events are performed. We selected only the
data from the first event to homogenize the sampling effort. In deeper and wider
streams (depth >= 0.7m), the sampling is
partial over the bank and the channel and it is performed by boat and by foot
(along the bank). We selected only the sampling done over the bank because the
channel was not systematically sampled. Two types of partial protocols takes
place: "partial over bank" and "partial by points", which are respectively
continuous and discrete samplings. We considered both types of partial protocols
in our analysis. In the "partial by point" protocol, the channel was sometimes
sampled as well, so we selected only the "partial by point" sampling in which
all the sampling points were done over the bank to homogenize the sampling. Some
sampled stations were located in streams with intermediate characteristics where
both "complete" and "partial" protocols were alternatively used depending on the
state of the stream at the time of sampling. For these sites, we only kept the
samples that had been carried out with the most frequently used protocol.

Heterogeneity in the sampling date may introduce variability due to different
climatic or environmental conditions but also to the life cycle of the species.
For instance, early surveys may precede the egg hatching and youngs-of-the-year.
In order to reduce heterogeneity in the sampling date, only one sampling per
year was retained if there were more in a given year, the one that had the most
species and then the most individuals. Finally, most of the fish sampling
occurred in September (Median: mid-August). There was low heterogeneity of the
sampling month within stations, with the median sampling month being mid-August
where the median standard deviation of the sampling month was  month, i.e. three
weeks. To further reduce sampling heterogeneity, we only kept the sampling in
which the length of stream sampled along the stream was inside the median length
sampled more or less 30%.

@@

Once the fishes have been caught, they are divided into different batches (Fig.
\@ref(fig:p-body-size)). Each batch contains only one species but individuals of
one species can be distributed in several batches. The body size of the fishes
is measured differently for each type of batch.  There are four types of
batches: N, I, S/L and G. The batches N and I contain the largest individuals.
In the N and I batches, the body size of all the individuals is recorded. The
batches S/L contain fishes of intermediate sizes. Inside each S/L batch, the
operator tries to make batches as homogeneous as possible in terms of body size.
Then, the body size of a subsample of at least 20 individuals is recorded. The G
batches contain individuals of small body size. In G batches, the body size of
the shortest and the largest individuals are recorded.

@@

Body size inference was guided by the recommendations of
the OFB agency, which has defined the sampling protocols, supervised the data
collection and performed analyses on the dataset for multiple purpose including stream
management. The database was obtained from the OFB agency.

@@

Batches that did not meet conditions regarding the number of individuals were
excluded.  We excluded batches for which the total number of individuals was not
recorded. We also excluded G batches for which $l_{min} \geq l_{max}$ or if at
least one of the measurement was missing. Additionally, a given G batch was
excluded when the number of individuals felt below 5, as G batches normally
contained more individuals. We excluded S/L batches for which the number of
measured individuals was inferior to 10, because it indicates a potential
problem in the batch. Finally, in the dataset used in the analysis, `r
na_length` individuals had missing length over `r nrow_fish_length` individuals,
and body size was inferred for these individuals.

@@

Some species were identified to subspecies, based on their morphotype, but they
belong to the same species based on fecundation criteria. We merged those
subspecies into one species. We merged 
`r length(unique(names(sp_to_replace())))` morphotypes into
`r length(unique(sp_to_replace()))` species.

@@

Diet information was obtained from fishbase.org and literature (Appendix A,
Table S2). The diet information contained from two to three life stages by
species, the life stages being defined by the body size of the fishes. Over the
57 fish species, only 7 had a piscivorous life stage and only three had a strict
piscivorous life stage. Fish species were then largely omnivorous.

@@

trophic_building_caption <- paste0( "Define trophic species and trophic
  interactions. (1) Each
  species is divided into 9 body size classes. We gathered data about
  the food diet of each fish species and how food diet varies according to
  ontogeny. (2) The life stage of a trophic species is determined by the
  median of the body size class, hereafter midpoint. A trophic link is set between the trophic
  species and the resources associated to this life stage. (3) For piscivorous
  trophic species, the trophic links among fishes are defined according to
  the predator/prey body size ratio. The predation window of a trophic
  species ranges from 3% to 45% of its midpoint. A trophic
  link is set between the predator trophic species and every trophic species whose
  midpoint of body size class range was included in the predation window.")

@@

```{r, cache = FALSE}
metaweb_caption <- paste0(
  "The metaweb describing the trophic interactions between all the 412 trophic species. Each trophic species is
  represented by a node and each color represents a species (S = 45). The 7 
  resource nodes are drawn in grey. The species names corresponding to the
  three digit codes are found in Table S1."
)
```

```{r metaweb, cache = FALSE, fig.cap=metaweb_caption}
knitr::include_graphics(mypath("manuscript", "bef_stability", "figs", "metaweb2.png"))
```

@@

Trophic interactions between the nodes of the metaweb were determined according to
the diet and the body size of the trophic species. We removed 
`r length(removed_sp_metaweb)` species because data about their diet was missing. It
represented  `r nrow(removed_ind_metaweb)` individuals over
`r nrow(length_sem_analysis)` individuals.

The life stage to which a trophic species belongs was determined by the median
of the body size range of the trophic species, each life stage being delimited
by a body size range. In return, this trophic species has trophic interactions
with the resource nodes of its life stage. The trophic interactions between a
predator and a prey were determined by the predator-prey body size ratio
[@brose_predator_2019; @poisot_structure_2016; @schneider_body_2012]. For a
given trophic species, we first determined if its body size range overlapped
with a piscivorous life stage (Fig. \@ref(fig:p-net-inf)). If the trophic
species was piscivorous, we determined its prey size range from 3% to 45% of the
median of its size range. A trophic interaction was set for each trophic species
whose corresponding size class median felt into the prey range of the predator
trophic species (Fig. \@ref(fig:p-net-inf)). To sum up, the metaweb contains
feeding interactions (1) between trophic species, (2) between trophic species
and resource nodes and (3) between resource nodes.

@@

The procedures to obtain altitude, slope, width and depth of the streams are fully
explained in main text. Because those measurements were collected during the
fishing protocol, they were easier to manage in the analyses. Then, we detail
in the following sections how water temperature, water flow and Biological
Oxygen Demand (BOD) variables were obtained. In the following section, we will
present how we averaged each variable to match the annual fish monitoring
events. We also detailed how we interpolated these variables to match the
spatial location of the fish samplings.

@@

We modelled each variable, i.e. water temperature, water flow and BOD, as dependant only on the covariation between
sites taking in account the stream network. The autocovariance between
sites was modelled with the linear-sill and mariah functions for taildown and tailup
autocovariance, according to their predictive performance. The interpolations
were done with the `SSN` R package [@isaak_applications_2014; @hoef_ssn:_2014].

@@

The CV of biomass over time can cover multiple temporal dynamics, including
increases, stable, decreases and a mix of them. Theoretically, however, the CV
computed to quantify stability is often represented with the assumption that the
overall dynamic of the biomass varies around an equilibrium
[@kefi_advancing_2019]. In order to approach the condition of equilibrium, we
kept only the stations that show no clear temporal trends. To characterise the
biomass temporal dynamics according to their trajectories, we used the symbolic
aggregated approximation method (SAX), which is commonly used in time series
analysis and implemented in the `jmotif` R package [@senin_grammarviz_2018].
This method classifies time series rather than quantifies trends. Therefore, it
is enough generic to encompass a diversity of temporal trajectories. The
classification necessitates three steps. The time series are first normalized.
Then, we reduced the dimensionality of the time series by a Piecewise
Aggregation Approximation (PAA) method. Each time series is divided into $N$
frames of equal size that allows to reduce the dimensionality of the time
series. For each frame, we simply kept the mean value of the time series.  The
final stage is to qualify each frame into string. Because values of normalized
time series typically follows a normal distribution ($N(0,1)$), a breakpoint can
be computed by dividing the area under the normal distribution in equal parts.
The algorithm attributes an alphabetic letter to each part from the lowest to
the highest ($a$, $b$, $c$, ...). We set three breakpoints, so $a$, $b$ and $c$.
Finally, the trajectory of each time series is classified as a combination of
$a$, $b$, $c$ letters. $abc$ and $cba$ time series represent respectively
monotonic increasing and decreasing trajectories. For data analysis, we kept
only the $bbb$ which represent time series that showed no temporal tendencies,
with respect to our methodology.

@@

```{r, cache = FALSE, fig.pos = "!H", out.extra = ""}
sem_variable_table <- tibble(
  Variable = c(paste0("PCA axis", seq(1, 2)), "Species richness", "Connectance", "Average trophic level", "Synchrony", "CVsp", "Total biomass"),
  Unit = c(rep("unitless", 2), "number by square meter", rep("unitless", 4), "gram by square meter"
    ),
  Transformation = c("Log base 10", "Log base 10 and inversion", "Log base 10", rep("No", 2), rep("Log base 10", 3)),
  Description = c("linked to stream size",
    "linked to average temperature and BOD",
    "Total species richness over the temporal series",
    "Median of annual link density", "Median of annual average trophic level",
    "Temporal synchrony in the dynamics of population biomass", "Average
    variability of population biomass", "Median of annual total biomass")) %>%
kable(
  format = "latex",
  booktabs = T,
  caption = "The description of the variables used in the structural equation models."
  ) %>%
kable_styling(latex_options = c("striped", "scale_down"))
sem_variable_table
```

\begin{table}
\caption{\label{tab:hyp-sem} Presentation of the links 
of the Structural Equation Models associated with the references supporting the links.}
\begin{center}
\begin{tabular}{ m{7cm}| m{1cm}| m{6cm}}
    \hline
    Link & sign & reference\\
    \hline
    PCA1 Avg stream size $\to$ Species richness & (+) & Galiana et al. (2018) \\
    \hline
    PCA2 Avg temperature $\to$ Species richness & (+/-) & Woods et al. (2020); Gauzens et al. (2020) \\
    \hline
    PCA1 Avg stream size $\to$ Connectance & (-) & Galiana et al. (2018) \\
    \hline
    PCA2 Avg temperature $\to$ Connectance & (+/-) & O’Gorman et al. (2019);
    Oksanen et al. (1981)\\
    \hline
    Species richness $\to$ Connectance & (-) & Winemiller (1989); Dunne (2006) \\
    \hline
    PCA1 Avg stream size $\to$ Avg trophic level & (+) & Post et al. (2000); Doi et al. (2009); McHugh et al. (2010) \\
    \hline
    PCA2 Avg temperature $\to$ Avg trophic level & (+/-) & O’Gorman et al. (2017)\\
    \hline
    Species richness $\to$ Avg trophic level & (+) & Schneider et al. (2016)\\
    \hline
    Species richness $\to$ Synchrony & (-) & Thébault and Loreau (2005); Loreau and de Mazancourt (2008); Thibaut and Connolly (2013) \\
    \hline
    Connectance $\to$ Synchrony & (+) & Thébault and Loreau (2005)\\
    \hline
    Avg trophic level $\to$ Synchrony & (+) & Raimondo et al. (2004); McCann and Rooney (2009) \\
    \hline
    PCA1 Avg stream size $\to$ Synchrony & (-) & Wang et al. (2019)\\
    \hline
    PCA2 Avg temperature $\to$ Synchrony & (?) & \\
    \hline
    Species richness $\to$ CVsp & (+) & Jiang et al. (2009)\\
    \hline
    Connectance $\to$ CVsp & (+) & Thébault and Loreau (2005)\\
    \hline
    Avg trophic level $\to$ CVsp & (-) & McCann and Rooney (2009); Shanafelt and Loreau (2018)\\
    \hline
    PCA1 Avg stream size $\to$ CVsp & (?) & \\
    \hline
    PCA2 Avg temperature $\to$ CVsp & (+) & Kratina et al. (2012); Fussmann et al. (2014)\\
    \hline
    CVsp $\to$ Biomass stability & (-) & Thibaut and Connolly (2013)\\
    \hline
    Synchrony $\to$ Biomass stability & (-) & Thibaut and Connolly (2013)\\
    \hline
    Species richness $\to$ Total biomass & (+) & Schneider et al. (2016)\\
    \hline
    Connectance $\to$ Total biomass & (+/-) & Thébault and Loreau (2003); Poisot
    et al. (2013)\\
    \hline
    Avg trophic level $\to$ Total biomass & (+) & Wang and Brose (2018)\\
    \hline
    PCA1 Avg stream size $\to$ Total biomass & (+) & Post et al. (2000); Allan and Ibanez Castillo (2009); Doi et al. (2009)\\
    \hline
    PCA2 Avg temperature $\to$ Total biomass & (+/-) & Kratina et al. (2012);
    Tabi et al. (2019)\\
    \hline
    \end{tabular}
\end{center}
\end{table}

@@

```{r, cache = FALSE}
hist_var_caption <- paste0(
  "Distribution of the variables included in the Structural Equation Models. The
  biomass stability, the CV of species (CVsp), PCA1, PCA2, species richness,
  synchrony and total biomass were logged. See Table S5 for the units."
)
```

```{r hist-sem-data, cache = FALSE, fig.cap = hist_var_caption}
sem_data %>%
  select(log_bm_std, log_rich_tot_std, log_sync, log_stab_std, log_cv_sp, log_RC1, log_RC2, t_lvl, ct) %>%
  gather(variable, value) %>%
  mutate(variable = str_replace_all(variable, get_sem_var_name_replacement())) %>%
  ggplot(aes(x = value)) +
  labs(y = "Values", x = "Frequency") +
  geom_histogram() +
  facet_wrap(~variable, scales = "free")
```

@@

```{r mod-res, fig.width = 7, fig.asp = 2, fig.cap = caption_mod_res, cache = FALSE}
library(nlme)
plot_lme_residuals <- function (x = NULL, main = NULL) {
  if (is.matrix(x$residuals)) {
    tb <- tibble(
      resid = x$residuals[, "fixed"], 
      fitted = x$fitted[, "fixed"]
    )
  } else {
    tb <- tibble(
      resid = x$residuals, 
      fitted = x$fitted
    )
  }

  ggplot(tb, aes(y = resid, x = fitted)) +
    geom_point() +
    labs(x = "Fitted values", y = "Residuals", title = main)

}
p_resid_stab_sem <- map2(mod_stab_list, names(mod_stab_list) , plot_lme_residuals)
plot_grid(plotlist = p_resid_stab_sem, ncol = 2)
```

@@

```{r, cache = FALSE}
est_stab_sem_caption <- paste0(
  "Estimates of the effects of the studied variables as predicted by the
  structural equation model on the temporal stability of annual community
  biomass. Avg: Average, Sdt.Error: Standard Error, DF: Degree of Freedom,
  P.Value: P-value, Std.Estimate: Standardised
  estimate. Significant standardised estimates are in bold."

)
format_coef_table(stab_sem_rich) %>%
  select(-Crit.Value) %>%
  mutate_if(is.numeric, round, digits = 2) %>%
  mutate(Std.Estimate = cell_spec(Std.Estimate, bold = ifelse(P.Value <= 0.05,
	T, F), format = "latex", escape = F)
    ) %>%
kable(
  format = "latex",
  booktabs = T,
  caption = est_stab_sem_caption,
  escape = F,
  digits = 2
  ) %>%
collapse_rows(columns = 1, valign = "top") %>%
kable_styling(latex_options = c("striped", "scale_down"))
```

```{r, cache = FALSE}
est_bm_sem_caption <- paste0(
    "Estimates of the effects of the studied variables as predicted by the
  structural equation model on the median of annual community
  biomass. Avg: Average, Sdt.Error: Standard Error, DF: Degree of Freedom,
  P.Value: P-value, Std.Estimate: Standardised
  estimate. Significant standardised estimates are in bold."
)

format_coef_table(bm_sem_rich) %>%
  select(-Crit.Value) %>%
  mutate_if(is.numeric, round, digits = 2) %>%
  mutate(Std.Estimate = cell_spec(Std.Estimate, bold = ifelse(P.Value <= 0.05, T, F))) %>%
kable(
  format = "latex",
  booktabs = T,
  caption = est_bm_sem_caption,
  escape = F, 
  digits = 2
  ) %>%
collapse_rows(columns = 1, valign = "top") %>%
kable_styling(latex_options = c("striped", "scale_down"))
```

@@

kable(formated_random_effects,
  format = "latex",
  booktabs = T,
  digits = 2,
  caption = caption_random_effect
  ) %>%
kable_styling(latex_options = c("striped"))
```

@@

```{r}
sens_cap <- paste0(
  "Sensivity analysis of the Structural Equation models for total biomass
  and its temporal stability."," The Constant dataset is the one keeping only the
  sites that does not show a clear temporal trend of community biomass; ", "Constant/
    without holes dataset kept only the constant sites plus the ones that had no
  holes in their sampling period; ", "Complete is the dataset containing all the
  sites that have been followed ten years or more;", " Without holes dataset is
  the complete dataset but containing only the sites that had no holes in their sampling period."
)
```
